Think again?\\ Optimal mental simulation tracks problem difficulty

### 2015-01-31 manuscript.tex
Add comparison of t=1 and t=2

%% What's already been done
\TODO{MOVE THIS TO THE DISCUSSION TO EXPLAIN THE LOW THRESHOLD WE FIND: According to previous research by \citeA{Vul:2014ba}, a sample-based agent should only take a small number of samples before making a judgment so long as there is any cost to taking samples---perhaps even just one. While taking a single sample clearly provides a worse chance of making a good decision than taking multiple samples, over the long run, taking a small number of samples maximizes expected utility across a large number of judgments. Does this story also hold true for mental simulations? There is some evidence that points to ``yes'': \citeA{Battaglia2013} analyzed the variability of people's responses in tasks concerning towers of building blocks, and found that participants seemed to use between three and seven samples per judgment.}

@@

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
        \caption{\textbf{Response times as a function of response.} \emph{Left:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color). \emph{Middle:} like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times. \emph{Right:} each point corresponds to a different stimulus, feedback type, and hole size.  The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.}
        \label{fig:pct-vs-rt}
    \end{center}
\end{figure*}

@@

The fitted model explained the data well, explaining both how accurate participants were for each trial (\HoleResponseCorr{}), and how quickly participants responded to trials (\HoleRTCorr{}, see Figure \ref{fig:model-results}).

\TODO{Can we show that accuracy correlation is better with SPRT softmaxing than strict accuracy to further suggest varying number of samples?}

@@

>>>>

@@

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
        \caption{\textbf{Response times as a function of response.} \emph{Left:} each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color). \emph{Middle:} like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times. \emph{Right:} each point corresponds to a different stimulus, feedback type, and hole size.  The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time. The black line indicates a 2nd-order polynomial fit between responses and response times and the shaded gray region indicates the 95\% confidence interval around the fit.}
        \label{fig:pct-vs-rt}
    \end{center}
\end{figure*}

@@

The fitted model explained participants' judgments of whether the ball would go in the whole very well (\HoleResponseCorr{}), and was additionally able to account for how quickly participants responded to trials (\HoleRTCorr{}, see Figure \ref{fig:model-results}). Even if the number of bounces is not included, the SPRT model with $T=2$ is able to account for a moderate amount of the variance in response times (\NoBouncesHoleRTCorr{}). In contrast, a simpler model that takes only a single sample each time (equivalent to SPRT with $T=1$) does slightly better at explaining people's responses (\RawHoleResponseCorr{}) but cannot explain the variation in response times beyond the number of bounces.

@@

\TODO{MOVE THIS TO THE DISCUSSION TO EXPLAIN THE LOW THRESHOLD WE FIND: According to previous research by \citeA{Vul:2014ba}, a sample-based agent should only take a small number of samples before making a judgment so long as there is any cost to taking samples---perhaps even just one. While taking a single sample clearly provides a worse chance of making a good decision than taking multiple samples, over the long run, taking a small number of samples maximizes expected utility across a large number of judgments. Does this story also hold true for mental simulations? There is some evidence that points to ``yes'': \citeA{Battaglia2013} analyzed the variability of people's responses in tasks concerning towers of building blocks, and found that participants seemed to use between three and seven samples per judgment.}
